---
title: "DataAnalysis"
author: "Yuxin Jin"
date: "4/12/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Description

*The goal of this Rmd script is to analyse patient data and make a heatmap for all genes with p value less than 0.01.*


## Step 1. Install and load libraries that might be useful

### 1. Install libraries
```{r}
install.packages("devtools")
install.packages("reshape2")
install.packages("plotly")
install.packages("ggplot2")
install.packages("dplyr")
```

### 2. Load libraries
```{r}
library(devtools)
library(reshape2)
library(plotly)
library(ggplot2)
library(dplyr)
```

## Step 2. Import the two big dataframe with all male and female data inside
```{r}
setwd("~/Desktop/TRGN510/FinalProject/Data")
Female.Data <- read.csv("FemaleData.csv",header = T, row.names = 1, stringsAsFactors = F)
Male.Data <- read.csv("MaleData.csv", header = T, row.names = 1, stringsAsFactors = F)
```

## Step 3. Merge two dataframe into one single dataframe
```{r}
Female.Data$gene <- rownames(Female.Data)
Male.Data$gene <- rownames(Male.Data)
Patient.Data <- left_join(Female.Data,Male.Data, by = "gene")
rownames(Patient.Data) = Patient.Data[,31]
Patient.Data = Patient.Data[,-31]
```
*For the merged PatientData, column 1-30 are female data, column 31-99 are male data.*

## Step 4. Log2 transform the data
```{r}
Patient.Log <- log2(Patient.Data+min(Patient.Data[Patient.Data>0]))
```

## Step 5. Run a t test and select data with p value less than 0.01

### 1. Run a t test
```{r}
Patient.Test <- apply(Patient.Data,1,function(x) t.test(x[c(1:30)],x[c(31:99)]))
T.test <- data.frame(t(sapply(Patient.Test,c)))
```

### 2. Add a column named p value to "Patient.Log"
```{r}
pvalue <- subset(T.test, select = "p.value")
pvalue$ID <- rownames(pvalue)
Patient.Log$ID <- rownames(Patient.Log)
Patient.Log <- left_join(Patient.Log, pvalue, by = "ID")
rownames(Patient.Log) <- Patient.Log[,100]
Patient.Log <- Patient.Log[,-100]
```

### 3. Select Genes with p value < 0.01
```{r}
SelectGene <- subset(Patient.Log, p.value < 0.01)
SelectGene <- SelectGene[,-100]
```

## Step 6. Create a heatmap for Gene selected

### 1. Melt the data, prepare for the heatmap
```{r}
SelectGene$ID <- rownames(SelectGene)
SelectGene.Melt <- melt(SelectGene, id.vars = c("ID"))
colnames(SelectGene.Melt) <- c("GeneID", "CaseID", "Expression")
```

### 2. Make an intereactive heatmap using ggplot2 and ggplotly
```{r}
GeneHeatmap <- ggplot(SelectGene.Melt , aes(x = GeneID, y = CaseID)) + geom_raster(aes(fill = Expression)) + scale_fill_gradient2(low="navy", mid="white", high="red", midpoint=0.5) + labs(x = "GeneID", y = "CaseID") + theme(plot.title = element_blank(),axis.text.x = element_blank(), axis.text.y = element_blank())
ggplotly(GeneHeatmap)
```

